SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-01-17 SI.tex
Update text
Update pdfs

\begin{table}[!h]
    \centering
    \begin{tabular}{c c}
    Abbreviation & Molecule name \\
    \hline
    POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
    POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
    POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
    POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
    PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
    PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
    DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
    DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
    DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
    DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
    DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
    DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
    DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
    DOG  & 1,2-dioleoyl-sn-glycerol \\
    DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
    DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
    DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
    DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
    DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
    DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
    SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
    DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
    SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
    POPI & \\ 
    SAPI & \\
    SLPI &  \\
    SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
    SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
    CER  & N-palmitoyl-D-erythro-sphingosine \\
    CHOL & cholesterol  \\
    DCHOL & 18,19-di-nor-cholesterol \\
    DHMDMAB & dihexadecyldimethylammonium  \\
    \hline
    POT & potassium ion  \\
    SOD & sodium ion  \\
    CLA & chloride ion \\
    CAL & calcium ion  \\
    CES & caesium ion \\
    SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecules used in the databank}
    \label{tab:abbreviations}
\end{table}

@@

\newpage
\section{Experimental data}
\subsection{NMR experiments}
Acyl chain order parameters of POPE and POPG were analyzed from the experiments that were used to determine headgroup order parameters in Ref.~\citenum{bacle21}. The analysis of the crowded spectral region at 29-31 ppm was based on the previous assignment reported for POPC membranes~\cite{ferreira13}.

>>>>

\begin{table}[!h]
    \centering
    \begin{tabular}{c c}
    Abbreviation & Molecule name \\
    \hline
    Lipids and surfactants & \\
    \hline
    POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
    POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
    POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
    POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
    PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
    PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
    DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
    DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
    DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
    DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
    DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
    DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
    DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
    DOG  & 1,2-dioleoyl-sn-glycerol \\
    DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
    DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
    DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
    DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
    DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
    DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
    SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
    DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
    SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
    POPI & \\ 
    SAPI & \\
    SLPI &  \\
    SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
    SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
    CER  & N-palmitoyl-D-erythro-sphingosine \\
    CHOL & cholesterol  \\
    DCHOL & 18,19-di-nor-cholesterol \\
    DHMDMAB & dihexadecyldimethylammonium  \\
    \hline
    Other molecules & \\
    \hline
    POT & potassium ion  \\
    SOD & sodium ion  \\
    CLA & chloride ion \\
    CAL & calcium ion  \\
    CES & caesium ion \\
    SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecules used in the databank}
    \label{tab:abbreviations}
\end{table}

@@

\newpage
\section{Experimental data}
\subsection{NMR experiments}
Acyl chain order parameters of POPE and POPG were analyzed from the experiments that were previosly used to determine headgroup order parameters~\cite{bacle21}. The analysis of the crowded spectral region at 29-31 ppm was based on the previous assignment reported for POPC membranes~\cite{ferreira13}.
